Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
Add discussion on the necessity and use of metadata

Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
The first layer, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
When making our science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
Provide a full description of all equipment used, *e.g.*, "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
This allows end-users to identify what was used and identify the methods used more accurately.
Just as importantly, this acknowledges the contributions of others whose works were instrumental in our research.
This also helps to ensure that we researchers can reconstruct what we have done since we will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on our research.

@@

Once it has been determined how to best manage the source code and the data sets for analysis, the next step is to consider how to share the data.
Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for us to deposit our data and generate a DOI for sharing the project once it is finished.

>>>>

Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
Making the raw data FAIR means providing proper metadata for the resource.
The metadata define the resource that has been made available allowing for discovery and use by other interested parties.
That is, proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
Properly constructed metadata allow for interoperability by allowing both humans and machines to understand what the materials are that are included in the resources and make use of them more easily.
Metadata also protects the resource and its future availability by tracking the resource's lineage, describing the resources physical characteristics and behavior so that it can be replicated using future technologies.
That is, without metadata, the data are not FAIR and the computational materials lose value by not having good documentation.

The first layer, as reported, is an essential step that is not substituted by the other practices and eventually researchers fail to provide sufficient description or correct citations.
When making our science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
Provide a full description of all equipment used, *e.g.*, "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
This allows end-users to identify what was used and identify the methods used more accurately.
Just as importantly, this acknowledges the contributions of others whose works were instrumental in our research.
This also helps to ensure that we researchers can reconstruct what we have done since we will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on our research.

@@

Once it has been determined how to best manage the source code and the data sets for analysis, the next step is to consider how to share the data.
Providers such as FigShare, Dataverse, OSF.io and Zenodo allow for us to deposit our data and provide metadata and generate a DOI for sharing the project once it is finished.
